Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})

### 2014-05-17 manuscript.tex
edits to results, tables, figures

\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{AJB}

@@

Genotype of the \emph{Hopscotch} insertion was confirmed with two PCRs for 837 individuals. Among the 247 maize landrace accessions genotyped, all but eight were homozygous for the presence of the insertion (Table~S1 and Table~S2). Within our \emph{parviglumis} and \emph{mexicana} samples we found the \emph{Hopscotch} insertion segregating in 37 and 4 populations, respectively, and at highest frequency in the states of Jalisco, Colima, and Michoac\'{a}n in central-western Mexico in both subspecies (\ref{Fig1Map}) \jri{the map only shows parviglumis. can we add mexicana? the text makes it seem as if both should be on the map}. We examined Hardy-Weinberg equilibrium in a total of 14 populations (10 \emph{parviglumis} and 4 \emph{mexicana}) with more than 8 individuals sampled per population. Three populations (RIMPA0073, RIMPA0093, and RIMPA0158) show evidence of deviations from expected genotype frequencies under the assumptions of HWE (p<0.05).  \jri{in what direction? too many hets? what's the F? } \lev{they weren't all in the same direction, do you still want me to list out?} \jri{no need to list all, but if there were sig. deviations in multiple directions in different pops, that is worth saying. maybe could list them all out in supp. table?}

\jri{please fix whitespace and black border on figure}
%Figure 1 Map 
%--------------------------------------------
\begin{figure*}[]
  \begin{center}
   \includegraphics[width=0.5\textwidth]{Fig1Map.pdf}
    \caption{Map showing the frequency of the \emph{Hopscotch} allele in populations of \emph{Zea mays} ssp. \emph{parviglumis} where we sampled more than 6 individuals. Size of circles reflects number of alleles sampled. } 
\label{Fig1Map}
  \end{center}
\end{figure*}
%--------------------------------------------

Using our \emph{Hopscotch} genotyping data, we calculated differentiation between populations (F\textsubscript{ST}) and subspecies (F\textsubscript{CT}) for populations in which we sampled 8 or more alleles. F\textsubscript{CT} is 0 within our dataset, and we found similar levels of F\textsubscript{ST} among populations within each subspecies (0.22) \jri{is this an average? this comes from libsequence?} and among all populations (0.23), to those reported in genome-wide estimates from previous studies \cite{Pyhajarvi2013} (\ref{Table1Fst}).

% Table 1
\begin{table}[htbp]
  \centering
  \caption{Pairwise F\textsubscript{CT} values from sequence and \emph{Hopscotch} genotyping data}
    \begin{tabular}{lccc}
 %   \toprule
    \multicolumn{1}{c}{\textbf{Comparison}} & \textbf{Seq. Region 2} & \textbf{Seq.  Region 1} & \textbf{\emph{Hopscotch}} \\
 %   \midrule
    EjuA \& EJuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.328 & 0.326 & 0.186 \\
    EjuA \& SLO & 0.258 & 0.416 & 0.28 \\
    EjuB \& MSA & 0.365 & 0.397 & 0.188 \\
    EjuB \& SLO & 0.29  & 0.512 & 0.28 \\
    MSA \& SLO & 0     & 0.007 & 0.016 \\
%    \bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}
Although we found large variation in \emph{Hopscotch} allele frequency among our populations, BayEnv analysis did not indicate a correlation between the \emph{Hopscotch} insertion and environmental variables (all Bayes Factors $<$ 1; \ref{TableS3BayEnv}).

>>>>

\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
%\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\renewcommand{\baselinestretch}{1.5}
\bibliographystyle{AJB}

@@

Genotype of the \emph{Hopscotch} insertion was confirmed with two PCRs for 837 individuals. Among the 247 maize landrace accessions genotyped, all but eight were homozygous for the presence of the insertion (Table~S1 and Table~S2). Within our \emph{parviglumis} and \emph{mexicana} samples we found the \emph{Hopscotch} insertion segregating in 37 and 4 populations, respectively, and at highest frequency in the states of Jalisco, Colima, and Michoac\'{a}n in central-western Mexico (Fig.\ref{Fig1Map}). We examined Hardy-Weinberg equilibrium in a total of 14 populations (10 \emph{parviglumis} and 4 \emph{mexicana}) with more than 8 individuals sampled per population. Three populations (RIMPA0073, RIMPA0093, and RIMPA0158) show evidence of deviations from expected genotype frequencies under the assumptions of HWE (p$<$0.05). \mbh{Jeff mentioned this needs to be fully reported in a supplementary table; alternatively we can just delete the result since we do not interpret or use it later in the manuscript.}
%Figure 1 Map 
%--------------------------------------------
\begin{SCfigure}[][t!]
  \centering \label{Fig1Map}
   \includegraphics[width=0.7\textwidth]{Fig1Map.pdf}
    \caption{Map showing the frequency of the \emph{Hopscotch} allele in populations of \emph{parviglumis} where we sampled more than 6 individuals. Size of circles reflects number of alleles sampled. } 
\end{SCfigure}
%--------------------------------------------

Using our \emph{Hopscotch} genotyping and \emph{tb1} resequencing data, we calculated differentiation between populations (F\textsubscript{ST}) and subspecies (F\textsubscript{CT}) for populations in which we sampled 8 or more alleles. We found that F\textsubscript{CT} = 0 within our dataset and levels of F\textsubscript{ST} among populations within each subspecies (0.22) \jri{is this an average? this comes from libsequence?} and among all populations (0.23) are similar to those reported genome-wide in previous studies (\citealt{Pyhajarvi2013}; Table \ref{Table1Fst}).

% Table 1
\begin{table}[htbp]
\rowcolors{2}{gray!25}{white}
  \centering
  \caption{Pairwise F\textsubscript{ST} values from sequence and \emph{Hopscotch} genotyping data}

    \begin{tabular}{lccc}\\\toprule
    \multicolumn{1}{c}{\textbf{Comparison}} & \textbf{Seq. Region 2} & \textbf{Seq.  Region 1} & \textbf{\emph{Hopscotch}} \\\midrule
    EjuA \& EJuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.328 & 0.326 & 0.186 \\
    EjuA \& SLO & 0.258 & 0.416 & 0.28 \\
    EjuB \& MSA & 0.365 & 0.397 & 0.188 \\
    EjuB \& SLO & 0.29  & 0.512 & 0.28 \\
    MSA \& SLO & 0     & 0.007 & 0.016 \\\bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}
Although we found large variation in \emph{Hopscotch} allele frequency among our populations, BayEnv analysis did not indicate a correlation between the \emph{Hopscotch} insertion and environmental variables (all Bayes Factors $<$ 1; \ref{TableS3BayEnv}).
